\begin{thebibliography}{00}

\bibitem{b1}
Daunis, Juergen: 'The automotive industry in transformation – business model disruption'\\
 https://www.ericsson.com/en/blog/2017/11/the-automotive-industry-in-transformation--business-model-disruption (abgerufen am 14.11.2019).

\bibitem{b2}
Logistik-info.de: 'Push und Pull Prinzip der Logistik'\\
https://www.logistik-info.net/diverses/push-vs-pull-prinzip/ (abgerufen am 16.11.2019)

\bibitem{b3}
Volkswagen: 'Modelle'\\
https://www.volkswagen.de/de/modelle-und-konfigurator.html (abgerufen am 16.11.2019)

\bibitem{b4}
Personas QUelle definition

\bibitem{b6}
Lex Fridman: https://lexfridman.com/ (abgerufen am 17.11.2019)

\bibitem{b7}
Martin Buehler, Karl Iagnemma, and Sanjiv Singh. 2009. e DARPA
urban challenge: autonomous vehicles in city traffic. Vol. 56. springer.
\bibitem{b8}
 Lex Fridman, Daniel E. Brown, Michael Glazer, William Angell,
Spencer Dodd, Benedikt Jenik, Jack Terwilliger, Julia Kindelsberger,
Li Ding, Sean Seaman, Hillary Abraham, Alea Mehler, Andrew Sipperley, Anthony Pettinato, Linda Angell, Bruce Mehler, and Bryan
Reimer. 2017. MIT Autonomous Vehicle Technology Study: LargeScale Deep Learning Based Analysis of Driver Behavior and Interaction with Automation. CoRR abs/1
\bibitem{b9}
Kieren McCarthy. 2018. So when can you get in the first self-driving
car? GM says 2019. Mobileye says 2021. Waymo says 2018. (May
2018). https://www.theregister.co.uk/2018/05/09/first autonomous
vehicles/
\bibitem{b10}
Alex Davies. 2015. Oh Look, More Evidence Humans Shouldn’t
Be Driving. (May 2015). https://www.wired.com/2015/05/
oh-look-evidence-humans-shouldnt-driving/
[9] Terrence Fong, Charles Thorpe, and Charles Baur. 2
\bibitem{b11}
Tom Vanderbilt and Brian Brenner. 2009. Traffic: Why We Drive the
Way We Do (and What It Says about Us) , Alfred A. Knopf, New York,
2008; 978-0-307-26478-7. (2009).
\bibitem{b12}
Raja Parasuraman and Victor Riley. 1997. Humans and automation:
Use, misuse, disuse, abuse. Human factors 39, 2 (1997), 230–253.
\bibitem{b13}
Thomas B Sheridan. 2002. Humans and automation: System design and
research issues. Human Factors and Ergonomics Society.

\bibitem{b14}
ADAC: https://www.adac.de/rund-ums-fahrzeug/ausstattung-technik-zubehoer/autonomes-fahren/grundlagen/autonomes-fahren-5-stufen/ (aufgerufen 17.11.2019)

\bibitem{b15}
Markus I. Reinke (2013): '30 Minuten Verkaufspsychologie'

\bibitem{b18}
https://medium.com/punchcut/ux-design-for-autonomous-vehicles-9624c5a0a28f

\bibitem{b19}
https://link.springer.com/content/pdf/10.1007\%2F978-0-85729-085-4.pdf, Seiten 1271-1310

\bibitem{b20}
https://iopscience.iop.org/article/10.1088/1757-899X/252/1/012096/pdf

\bibitem{b21}
Bertoncello M and Wee D 2015 Ten ways autonomous driving could redefine the automotive
world. McKinsey\&Company http://www.mckinsey.com/industries/automotive-andassembly/our-insights/ten-ways-autonomous-driving-could-redefine-the-automotive-world 

\bibitem{b22}
https://www.gruenderszene.de/lexikon/begriffe/usability?interstitial

\bibitem{b23}
https://www.usability.gov/what-and-why/user-centered-design.html

\bibitem{b24}
https://www.seobility.net/de/wiki/User\_Centered\_Designs

\bibitem{b25}
Automatisierung - Von Fahrerassistenzsystemen zum automatisierten Fahren - VDA

\bibitem{b26}
https://www.focus.de/auto/autoentwicklung/bellbergs-auto-klartext-sorgen-autonome-autos-fuer-das-bedingungslose-grundeinkommen\_id\_10794360.html

\bibitem{b27}
https://www.manager-magazin.de/unternehmen/autoindustrie/selbstfahrendes-kfz-mensch-vs-maschine-wer-gefahren-besser-erkennt-a-1200362.html

\bibitem{b28}
https://www.autonomes-fahren.de/musk-tesla-faehrt-autonom-zum-ende-des-jahres/

\bibitem{b29}
https://waymo.com/lidar/

\bibitem{b30}
Christian Ress, Martin Wiecker - Potenzial der V2X-Kommunikation für Verkehrssicherheit und Effizienz; (im abstract)

\bibitem{b31}
Brian Reimer, PhD; MIT (ZITAT Youtube Video)

\bibitem{b32}
https://t3n.de/news/tesla-statistik-unfaelle-autopilot-1136864/

\bibitem{b33}
UPTANE - Security and Customizability of Software Updates for Vehicles; Trishank Karthik Kuppusamy, Lois Anne DeLong and Justin Cappos

\bibitem{b34}
https://www.youtube.com/watch?v=jTio\_MPQRYc\&t, Jeff Schneider Vortrag

\bibitem{b36}
https://link.springer.com/content/pdf/10.1007\%2Fs11623-017-0764-5.pdf\\

\end{thebibliography}

